Modeling Liver with Glisson's Capsule in Real-Time Medical Simulations

### 2013-05-31 Doc/Vrst2013/vrst2013.tex
FIX: conclusions
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@589 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\section{Conclusions and Future Work} %{{{

In the paper we presented a liver model accounting for the Glisson's capsule, a component that is often overlooked. Each constituent being modelled with a different type 
of finite elements: tetrahedral corotational model used for the parenchyma and
and CST membrane elements used for the capsule. 
The model was validated in the context for local displacements based on the the aspiration test presented in~\cite{Hollenstein2006}. The aspiration test
was successfully reproduced, showing a good agreement between the simulation and experiments.

Presently we are focusing on the validation of the model also in context of
global deformations of the organ where we believe the capsule also plays an
essential role. This task is however complicated by the lack of biomechanical
literature dealing with the response of the capsule.

>>>>

\section{Conclusions and Future Work} %{{{
In the paper we presented a model of tissue with capsule based on two separated models for parenchyma (corotational tetrahedral elements)
and membrane (CST triangular elements). Employing a simulation scenario known as aspiration test, 
we compared the model with experimental data provided in the literature 
and verified the results obtained in the simulation w.r.t. to a standard computationally expensive model based entirely on volume elements~\cite{Hollenstein2006}. We obtained values which were in good correspondence with results reported in the literature.

Presently we are focusing on the validation of the model also in context of
global deformations of the organ where we believe the capsule plays an
essential role as well. This task is however complicated due to the limited number of experimental studies dealing with 
both the parenchyme and the capsule.
